Online {\IterComp}

### 2017-11-17 related.tex
work and related minor

Chen~\etal~\cite{chen10,chen12a} show that the best optimization options, however, can differ across inputs. Their results suggest that, in
most cases it is possible to find a single set of optimizations that produces good results across all inputs; but achieving this requires
developers provide a few tens of representative inputs to be used by the iterative compilation search process. We argue that providing
representative inputs is difficult in practice, as users may not use the applications as the developer expects. Even if this is possible,
current approaches all require to evaluate all candidate compiler options on the same input. Doing so across a range of inputs would incur
significant overhead, which thus prevents iterative compilation to be adopted at a larger scale.

@@

Some approaches attempt to drive \itercomp with execution time information~\cite{fursin:hal-01257279,fursin:inria-00001054,tiwari2011online}. They create
multiple versions of the hottest procedures, optimized and unoptimized, and they evaluate them at runtime on different invocations.
For each invocation, they record the time spent in the procedure and the version used. By comparing the average time required for each
invocation, they are able to evaluate the relative performance of different optimizations. The limitations of such approaches are that they
depend on the amount of work performed by the procedure not changing dramatically from invocation to invocation and the number of
invocations being sufficiently high to collect multiple data points for each version. These drawbacks keep it from being a general solution
to the problem of iterative compilation.

>>>>

Chen~\etal~\cite{chen10,chen12a} show that the best optimization options, however, can differ across inputs. Their results suggest that, in
most cases it is possible to find a single set of optimizations that produces good results across all inputs; but achieving this requires
developers provide a large number of representative inputs to be used by the iterative compilation search process. We argue that providing
representative inputs is difficult in practice, as users may not use the applications as the developer expects. Even if this is possible,
current approaches all require to evaluate all candidate compiler options on the same input. Doing so across a range of inputs would incur
significant overhead, which thus prevents iterative compilation to be adopted at a larger scale.

@@

Some approaches attempt to drive \itercomp with execution time information~\cite{fursin:hal-01257279,fursin:inria-00001054,tiwari2011online}. They create
multiple versions of the hottest procedures, optimized and unoptimized, and they evaluate them at runtime on different invocations.
For each invocation, they record the time spent in the procedure and the version used. By comparing the average time required for each
invocation, they are able to evaluate the relative performance of different optimizations. The limitations of such approaches are that they
depend on the amount of work performed by the procedure not changing from invocation to invocation and the number of
invocations being sufficiently high to collect multiple data points for each version. These drawbacks keep it from being a general solution
to the problem of iterative compilation.

### 2017-11-17 work.tex
minor comments
overall changes
minor changes
work and related minor

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figs/corr_coeff.pdf}
    \caption{Correlation coefficients between the work metric ($\Delta W$) and the execution time of the unoptimized version for each benchmark.}
    \label{fig:motivation-speedups}
\end{figure*}

@@

    Optimal instrumentation significantly reduces the profiling overhead when compared to na\"ive instrumentation, from an average overhead
    of 79\% to 13\%. Still, 13\% slowdown might be more than what the user is ready to tolerate, while for isolated case the overhead might
    be as high as 60\%. We need to reduce overhead further to make the work metric practical.

@@

    The \WCRelaxLower relaxation error guarantees are hard but also too conservative. It assumes that each loop will always execute the
    path with the minimum amount of work possible, which might be orders of magnitude less than the work actually performed. When this is
    the case, we end up with a relative error much lower than intended and a profiling overhead unnecessarily high. Our second, more
    aggressive, strategy avoids this problem, by estimating the error and overhead contributions of each probe in relation to the whole
    program.

>>>>

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/corr_coeff.pdf}
    \caption{Correlation coefficients between the work metric ($\Delta W$) and the execution time of the unoptimized version for each benchmark.}
    \label{fig:motivation-speedups}
\end{figure*}

@@

    Optimal instrumentation significantly reduces the profiling overhead when compared to na\"ive instrumentation, from an average overhead
    of 79\% to 13\%. Still, 13\% slowdown might be more than what the user is ready to tolerate, while for isolated cases the overhead might
    be as high as 60\%. We need to reduce overhead further to make the work metric practical.

@@

    The \WCRelaxLower relaxation error guarantee is hard but also too conservative. It assumes that each loop will always execute the
    path with the minimum amount of work possible, which might be orders of magnitude less than the work actually performed. When this is
    the case, we end up with a relative error much lower than intended and a profiling overhead unnecessarily high. Our second, more
    aggressive, strategy avoids this problem, by estimating the error and overhead contributions of each probe in relation to the whole
    program.
